paper1_figures

### 2023-09-21 paper1_markdown.Rmd
Update paper1_markdown.Rmd
change intro

@@

**??? CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998) The study of cooperation is particularly interesting in social dilemmas, i. e. situations in which short-term individual and long-term collective interests are at odds [@Hardin1968]. add Dawes' definition

where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980]. **\<- EXPLAIN BETTER!!!**

>>>>

Many societal problems that humans are facing nowadays are social dilemmas, i. e. situations in which short-term individual and long-term collective interests are at odds [@Hardin1968]. More specifically, independently of others' actions, every individual obtains a better individual payoff by acting in an egoistic, non-cooperative way. However, if everybody did so, the worst possible outcome is obtained ????

where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980].

@@

**??? CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998)  **\<- EXPLAIN BETTER!!!**
